Blocking-resistant communication\\through domain fronting

### 2014-07-25 docs/meek.tex
Update caption.
Partial revision of architecture section.

The components of the system are shown in Figure~\ref{fig:architecture}.
The three parts that are new in our system are:
\begin{enumerate}
\item The client program \meekclient.
Using the pluggable transports protocol, Tor treats \meekclient\ as a SOCKS proxy.
When \meekclient\ receives data from Tor, it bundles it up in an HTTP POST
request and sends it to the web app,
using HTTPS to hide the contents and the domain fronting trick to hide the true destination.
Downstream data are returned in HTTP responses, which \meekclient\ decodes and sends back to Tor.
\item The ``reflector'' web app, running on App Engine.
Its domain name \mbox{meek-reflect.appspot.com} is protected by domain fronting.
It is called a reflector because it doesn't do anything intelligent:
it merely copies the HTTP requests it receives and forwards them
to \meekserver\ running on the Tor bridge.
\item The server program \meekserver, which acts as an HTTP server.
It receives reflected requests from the web app, decodes their bodies,
and forwards the contents to an instance of Tor running on the same host.
If there is anything pending to be sent back to the client,
\meekserver\ sends it along with its HTTP response.
\meekserver\ also takes care of stringing together multiple HTTP requests
into one logical stream and multiplexing multiple concurrent connections,
both using the technique of session IDs described in this section.
\end{enumerate}

The main technical challenge in making this system work
is in encoding a TCP stream as a sequence of HTTP requests and responses.
\meekserver\ handles many clients at once, and their data streams
are split across multiple HTTP transactions.
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but we cannot do that because streams are split across multiple TCP sessions.
Rather, each instance of \meekclient\ generates at startup a random 32-byte
session ID, which is sent along with its requests in a special
X-Session-ID HTTP header.
\meekserver, when it sees a particular session ID for the first time,
opens up a new connection to the local Tor process,
and stores the session ID in a cache. Subsequent requests with the
same session ID will reuse the same Tor connection.
Entries are removed from the cache after a period of inactivity.

% Use a child's garden--like figure of the HTTP protocol here.
% "concatenates successive bodies"

HTTP is fundamentally a pull-based protocol.
There is no way for the server to send data to the client without
the client first making a request.
The same applies to meek: when \meekserver\ has data to send back to
a client with a particular session ID, it cannot do so until it
receives a request from that client.
For this reason, \meekclient\ polls the server,
sending an empty request if necessary, every so often.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
Alternative techniques for push-like behavior,
such as HTTP long polling,
don't work well with App Engine,
because App Engine requires requests to finish within 60 seconds.

@@

\begin{figure}
\centering
\includegraphics[height=1.5in]{browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless instance of the browser runs in the background and is invisible to the user.
This figure is a detailed view of the ``User's PC'' component of Figure~\ref{fig:architecture}.
}
\label{fig:browser-architecture}
\end{figure}

@@

>>>>

The components of the system are shown in Figure~\ref{fig:architecture}.
The parts that are new in meek
are the programs \meekclient\ and \meekserver,
which are the pluggable-transports~\cite{pt} interface between Tor and meek.
% All the programs are free software, naturally,
% and may be downloaded from the meek home page at
% \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.

\meekclient\ is essentially a web client that knows how to front HTTPS requests.
When \meekclient\ receives data from a client Tor process, it bundles it up into a POST request
and fronts the request through the web service
(which in turn forwards it to \meekserver\ on the bridge).
If the response contains any payload, \meekclient\ decodes it and returns it back to Tor.
\meekclient\ takes pains to make its TLS fingerprint
look like that of a browser; see Section~\ref{sec:browserextension}.

\meekserver\ is a special-purpose web server.
When \meekserver\ receives a request, it extracts the body and feeds it into
a local Tor running as a bridge.
If there are any data pending to be sent back to the client from Tor,
\meekserver\ includes it in the body of the HTTP response.
\meekserver\ also handles session management:
as there may be many clients using the service at once,
the server must determine which client session each incoming request belongs to.
% It does this by means of an X-Session-ID header,
% described in this section.

When meek is used with Google App Engine, one other component is needed.
It is a small ``reflector'' web app that simply copies any request
it receives and forwards it to an instance of \meekserver\ running on a bridge.
App Engine cannot directly run a Tor bridge,
so we bounce the requests to somewhere that can.
The reflector app emulates the behavior of an origin-pull CDN,
which also simply copies and forwards a request to the origin server
when the response is not already cached.

The main technical challenge is handling a TCP stream
that has been split up into a sequence of HTTP requests and responses.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
\meekserver\ must handle many clients at once,
and therefore maintains many open connections to the local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for meek for two reasons:
the source IP of the requests is that of the intermediate web service,
not that of the client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Rather, each client generates a random 256-bit session ID,
which it sends with each of its requests in a special
X-Session-ID header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows an sample of the protocol.

\begin{figure}
% Use a child's garden--like figure of the HTTP protocol here.
\caption{
The meek protocol.
The session ID is randomly generated by the client.
The protocol shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor is unable to classify the traffic based on the
Host or X-Session-ID headers.
}
\label{fig:protocol}
\end{figure}

% out of order, blah blah.
% "concatenates successive bodies"
% handle it by strict serialization, has performance issues, see ...

HTTP is fundamentally a pull-based protocol.
There is no way for the server to send data to the client without
the client first making a request.
The same applies to meek: when \meekserver\ has data to send back to
a client with a particular session ID, it cannot do so until it
receives a request from that client.
For this reason, \meekclient\ polls the server,
sending an empty request if necessary, every so often.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
Alternative techniques for push-like behavior,
such as HTTP long polling,
don't work well with App Engine,
because App Engine requires requests to finish within 60 seconds.
% Psiphon did it.

@@

\begin{figure}
\centering
\includegraphics[height=1.5in]{browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless instance of the browser runs in the background and is invisible to the user.
This figure is a detailed view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
}
\label{fig:browser-architecture}
\end{figure}

@@

% meek apart from Tor.
% more risk for the proxy operator
% can require people to run their own proxies à la GoAgent.
% "Censorship implies surveillance"
